Duplicate Question Detection using Online Learning

### 2016-11-27 paper/main.tex
fixed table

\begin{table}[h!]
\centering
\caption{Statistics of the Training and the Test Set.}
 \begin{tabular}{|l c c |}
 \hline
 Dataset & \#Similar Label & \#All \\ [0.5ex]
 \hline\hline
 Training Stackoverflow & 1238 & 62499 \\
 \hline
 Testing Stackoverflow & 258 & 10398  \\
 \hline
 Training Reddit & 114 &   676 \\
 \hline
 Testing Reddit & 23 & 139  \\
 \hline
\end{tabular}

@@

\begin{table}[h!]
\centering
\caption{Recall rate for both datasets.}
 \begin{tabular}{|l r |}
 \hline
 Dataset & Recall Rate  \\ [0.5ex]
 \hline\hline
 Stackoverflow & 76.87\%  \\
 \hline
 Reddit & 80.59\%  \\
 \hline
\end{tabular}

@@

\begin{table}[h!]
\centering
\caption{Recall rate for both datasets using different supervised models.}
 \begin{tabular}{|l l r|}
 \hline
 Dataset & Model & Recall Rate  \\ [0.5ex]
 \hline\hline
 Stackoverflow & Random Forest & 76.87\%  \\
 Stackoverflow & Logistic Regression & 37.12\%  \\
 \hline
  Reddit & Random Forest & 80.59\%  \\
  Reddit & Logistic Regression & 10.84\%  \\
 \hline
\end{tabular}
\end{table}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{picture}}]{Chapman Siu}
is Masters candidate from Georgia Institute of Technology. Chapman is also a lion.
\end{IEEEbiography}

>>>>

\begin{table}[!t]
\centering
\caption{Statistics of the Training and the Test Set.}
 \begin{tabular}{l r r } 
 \hline
 Dataset & \#Similar Label & \#All \\ 
 \hline
 Training Stackoverflow & 1238 & 62499 \\ 
 %\hline
 Testing Stackoverflow & 258 & 10398  \\
 %\hline
 Training Reddit & 114 &   676 \\
 %\hline
 Testing Reddit & 23 & 139  \\
 \hline
\end{tabular}

@@

\begin{table}[!t]
\centering
\caption{Recall rate for both datasets.}
 \begin{tabular}{l r } 
 \hline
 Dataset & Recall Rate  \\ 
 \hline
 Stackoverflow & 76.87\%  \\

 Reddit & 80.59\%  \\
 \hline
\end{tabular}

@@

\begin{table}[h!]
\centering
\caption{Recall rate for both datasets using different supervised models.}
 \begin{tabular}{|l r r|} 
 \hline
 Dataset & Model & Recall Rate  \\ [0.5ex] 
 \hline\hline
 Stackoverflow & Random Forest & 76.87\%  \\
 Stackoverflow & Logistic Regression & 37.12\%  \\
 \hline
  Reddit & Random Forest & 80.59\%  \\
  Reddit & Logistic Regression & 10.84\%  \\
 \hline
\end{tabular}
\end{table}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{picture}}]{Chapman Siu}
is a Masters candidate from Georgia Institute of Technology. Chapman is also a lion.
\end{IEEEbiography}
